A New, Larger Sample of Supernova Remnants in NGC\,6946

### 2019-01-15 ms.tex
Near final draft ready for properly naming figures

@@

\title{An New Search for Supernova Remnants in NGC\,6946}

@@

The relatively nearby spiral galaxy NGC~6946 is one of the most actively star forming galaxies in the local Universe.  Ten supernovae have been observed since 1917, and hence NGC~6946 surely contains a large number of supernova remnants (SNRs).  
Here we report a new optical search for these SNRs in NGC~6946 using narrow-band images obtained with the WIYN telescope to 
identify 147 emission nebulae 
as likely SNRs,  based on elevated \sii:\ha\ ratios compared to \hii\ regions.  We have obtained spectra of 102 of these emission nebulae with Gemini North--GMOS; of these, 89 have \sii:\ha\ ratios greater than 0.4.  All but one of the 27 SNR candidates identified earlier by Matonick \& Fesen (1997) are contained in our sample.  However, there is very little overlap in our sample between the SNR candidates identified by Bruursema et al. (2014) from \feii\ imagery or by Lacey et al. (2001) from radio data.  Very few of the SNR candidates are X-ray sources, unlike the situation in some other galaxies such as M33 and M83, possibly due to  more reddening along the line of sight to NGC~6946.  The emission line ratios, e.g., \nii:\ha\ of the candidates in NGC~6946 are fairly typical of those observed in SNR samples from other galaxies with comparable metallicity.  
Two of the historical supernovae were detected as young optical SNRs showing high velocity ejecta. None of the other candidates observed spectroscopically show evidence of anomalous abundances or evidence of significant velocity broadening in our low resolution spectra.

@@

Optically, SNRs are usually identified on the basis of high \sii:\ha\ ratios compared to \hii\ regions.  In bright \hii\ regions, most S is found in the form of S$^{++}$ or S$^{+++}$, and as a result the \sii:\ha\ ratios are typically 0.1 or smaller.  In SNRs, where emission is driven by impulsive heating from shock waves, S$^+$ is found in an extended recombination and cooling zone behind the shock, and the \sii:\ha\ ratios are typically $\gtrsim0.4$.  The diagnostic can become less deterministic at lower surface brightness, as recently discussed by \cite{long18} for the case of M33.

The first optical search for SNRs in \gal\ was made by \cite{matonick97}, hereafter MF97, who used interference filter imagery to identify 27 emission nebulae with \sii:\ha\ ratios $\geq$ 0.45 as SNRs.  One of these sources, MF97-16, was, later associated with the ultraluminous black hole X-ray binary NGC~6946 X-1 \citep{roberts03}. Though very rare, such ultra-luminous X-ray sources (ULXs) have  the hard X-ray spectra that produce line ratios in the surrounding circumstellar ISM that resemble those expected from SNRs. To our knowledge, no other optical searches for SNRs in NGC~6946 exist, nor have spectra of the remaining MF97 objects ever been reported.

\hii\ regions and SNRs also radiate at radio wavelengths.  SNRs typically have steep non-thermal radio spectral indices arising from synchrotron radiation, whereas \hii\ regions have relatively flat thermal spectra arising from free-free and recombination radiation. \todo{KSL to check previous assertion}  At radio wavelengths, SNRs in nearby galaxies are generally identified as non-thermal radio sources associated with optical \ha\ emission.  (This association criterion arises because many background radio sources---typically active galaxy nuclei (AGNs)---also have non-thermal spectra, and like AGNs, the SNRs are generally unresolved in radio images of galaxies beyond the Local Group.)  In the case of \gal,  \cite{lacey01} identified 35 radio-selected SNR candidates on the basis of these criteria, none of which overlap with the MF97 list of optical candidates.  Their radio candidates were located in the brightest parts of the spiral arms of \gal; Lacey \& Duric suggested that the reason the two lists do not overlap is primarily due to selection effects.

Here we discuss a new, more sensitive optical search for SNRs in \gal\ in which we identify a total of 147 SNR candidates using interference filter imagery.  We also discuss spectroscopic observations of 102 of these candidates, which we use to verify the ratios obtained from the imaging and to characterize other characteristics of our new optical sample.  The paper is organized as follows:  Section 2 describes both our imaging and spectroscopy observations,  presents our much-expanded catalog of optical SNR candidates, and the results of our spectroscopy that has confirmed many of these.  Section 3 discusses these results in the context of both \gal\ and other spiral galaxies, and Section 4 provides a brief summary of our results.

@@

We carried out narrow-band imaging observations of \gal\ from the 3.5m WIYN telescope and MiniMosaic imager on Kitt Peak on the nights of 2011 June 26-28 (UT).\footnote{The WIYN Observatory is a joint facility of the University of Wisconsin-Madison, Indiana University, the National Optical Astronomy Observatory and the University of Missouri.}  The so-called ``Minimo'' was mounted at the f/6.3 Nasmyth port and consisted of a pair of $2048\times4096$ SITe chips, with a field  9\farcm 6 square at a scale of 0\farcs 14 pixel$^{-1}$.  We used interference filters that pass lines of \ha, \sii \lamlam6716,6731, and \oiii \lam 5007, plus red and green narrow-band continuum filters so we could subtract the stars and produce pure emission-line images. Frames in each filter were dithered to enhance removal of cosmic rays and bad pixels.  Further observational details are given in Table 1.  It is noteworthy that the \ha\ filter has quite a narrow bandwidth, 27\ \AA\ FWHM. Its transmission is 69\% at the rest wavelength of \ha, but only 11\% at 6548\ \AA\ and 16\% at 6583\ \AA; hence, the \nii\ lines are greatly attenuated relative to \ha.\footnote{The recessional velocity of \gal\ is only $40 \kms$, so the lines are redshifted by $\lesssim 1$ \AA.}  This facilitates identification of SNRs based on their image-derived \sii:\ha\ ratios.  Seeing throughout this run was about $1\arcsec \approx 32$ pc at the distance of \gal.  While sufficient for identifying SNRs in all but the most crowded regions, this resolution could provide only crude diameter estimates and only for the larger objects.

We used standard IRAF\footnote{IRAF is distributed by the National Optical Astronomy Observatory, which is operated by the Association of Universities for Research in Astronomy, Inc., under cooperative agreement with the National Science Foundation.} techniques for processing the images, including overscan correction, bias subtraction, and flat-fielding using dome flats.  Procedures in the IRAF {\texttt mscred} package were then used to combine the data from the individual chips into a mosaic image for each frame, assigned a WCS for each using stars from the USNOB1 catalog (WPB: ref needed?).  We then stacked  all the images by filter onto an arbitrary standard coordinate system with a scale of 0\farcs 20 pixel$^{-1}$ and scaled and subtracted the continuum images from the emission-line ones (red from \ha\ and \sii; green from \oiii) to give pure emission-line images with most of the stars and galaxy background light removed.  Finally, we used observations of several spectrophotometric standard stars from the catalog of \citet{massey88} to flux calibrate the emission-line images.  Figure \ref{fig_overview} shows a color version of the final images (R = \ha, G = \sii, B = \oiii).

\todo[inline]{For the Overview Figure, ksl and wpb like the version that shows the galaxy light (currently Fig. 2).  Frank is responsible for updating the overview figures, and describing them in the text.}

@@

To select SNR candidates, we used the DS9 display program to show the continuum-subtracted WIYN images in all three emission lines as well as a \sii:\ha\ ratio image and a continuum image (to discriminate stars or stellar subtraction residuals from point-like nebulae).   We then visually inspected these to select SNR candidates based on a high \sii:\ha\ ratio.  The initial inspection was carried out by Middlebury undergraduate Marc DeLaney; subsequently two of us (WPB and PFW) compiled independent candidate lists; we then conferred to agree on a consensus list of 147 candidates, including the 27 from MF97.

Figure \ref{fig_diagnostic} shows an example for a small region $\sim$1.5\arcmin\ south of the nucleus containing two of the MF97 objects and several new SNR candidates. In this example we have combined the three star-subtracted emission line images into a single color panel that shows how the stronger \sii\ and/or \oiii\ emission from the SNR candidates makes them stand out.  The \sii:\ha\ ratio image was a key diagnostic for drawing our eyes to potential objects of interest. Then an assessment of the integrity of the candidate as an emission object was made by inspection of the actual images.  This was done to separate candidates from stellar residuals or false regions of higher ratio in the ratio map that were due to noise.

Having performed similar SNR searches in other galaxies such as M33 and M83, it is worth noting some differences for \gal.  M33 is of course much closer, and the nebulae of interest are almost always resolved.  M83 is much more distant (4.6 Mpc) than M33, but our search there was aided by the exceptional seeing conditions we obtained at the Magellan telescope (0.5\arcsec).  Many objects were resolved, but others extended down to the limits of what even HST could resolve ($\sim$1-2 pc).  Our WIYN survey of \gal\ did not have exceptional seeing, and the distance is some 50\% larger than for M83.  Hence, relatively few of the nebulae of interest are resolved, and with variations in the complex galaxy background, it is much more difficult to perform a systematic search.  The use of the \sii:\ha\ ratio image was particularly helpful for \gal, which is the most distant galaxy for which we have performed this kind of SNR survey. Nonetheless, while we have expanded the SNR candidate list very substantially, clearly completeness has not been achieved.  Our list of 147 SNR candidates falls far short of M83, for example, even though the SN rate is larger in \gal.  Higher resolution data (better seeing and/or HST imaging) would no doubt help substantially, but the greater distance is still a limiting factor.

In addition, we initially selected 51 objects with relatively high \oiii:\ha\ ratios (using an \oiii:\ha\ ratio image in the display), in an attempt to identify young, ejecta-dominated SNRs such as Cas A in the Galaxy. With ten SNe in the last century, one might expect a number of young, ejecta-dominated SNRs to be present.  Though none of the O-selected candidates had ratios as extreme as seen for Cas A or 1E0102-72.3 in the Small Magellanic Cloud, we nevertheless selected some of these for follow-up spectroscopy.  The vast majority of these nebulae turned out to be \hii\ regions with somewhat enhanced ionization state, and so these form the bulk of the \hii\ sample we use for comparison below. Finally, we inspected the positions of the nine\footnote{As of the 2011 observations there were nine SNe; a tenth SN was recorded in 2017.} historical SNe in \gal\ for evidence of nebular emission; we only detected line emission at the positions of SN1980K and SN2004et, both of which we targeted for follow-up spectroscopy.

%\todo[inline]{ksl - It might be worthwhile to have a few sentences of comparison here to our work on M83 where the Magellan seeing made if far easier to see extended emission, and in M33 of course where all of the SNRs are resolved.  This is about the limit of what we can do from the ground, particularly with the seeing we had with WYIN.  To do better, one needs better seeing.  WPB: I tried to incorporate these points into the text added above with the exmaple diagnostic figure.}

The SNR candidates are listed in Right Ascension order in Table \ref{table_candidates}.  For each candidate, we provide (1) a source name, (2) the name of the source in MF97 if any,  (3,4) the position  (J2000), (5) the deprojected galactocentric distance (GCD), (6) the \ha\ flux as derived from the emission line images, (7) the \sii:\ha\ ratio measured from the images, (8) the spectrum we used to confirm the imaging ratios (see below), and (9) whether or not the object has a spectroscopic confirmation that the  \sii:\ha\ ratio is $\ge$ 0.4 (see below).

\todo[inline]{We need a consistent story about the HII regions.  We mention that we selected some O3 objects.  We got spectra of 24 of these.   We have another 41 spectra of HII regions along the slit.  We got very few HII regions just by chance, though these are included in the 41.  It's hard to actually parse out the history of which are which.  WPB: Note that I added some words above in the ``[O III] object" discussion to at least partially address this concern.}

@@

We used the Gemini Multi-Object Spectrograph (GMOS) on the 8.2m Gemini-North telescope to obtain all the spectra reported here, during queue-scheduled programs in semesters 2014B (program GN-2014B-Q-83) and 2015B (program GN-2015B-Q-91).  
For the 2014B program, we designed six custom masks, each with 20-30 slitlets targeting SNR candidates whose positions we determined from our 2011 WIYN images, together with  short $R$-band pre-images of several \gal\ fields taken with GMOS earlier in 2014 as part of the spectroscopy preparation program.    
We used two additional masks (which we refer to as masks 7 and 8 for simplicity)  for the 2015B program.  Slitlets in one or more of our eight masks were placed on 102 distinct SNR candidates, including ones with a range of sizes, GCDs, and ISM environments (locations in arms and in 
inter-arm regions).  In addition to the SNR candidates, we also placed a number of slitlets on prominent \hii\ regions for comparison purposes in both 2014 and 2015.
Figure \ref{fig_overview} shows all the SNR candidates from the sample for which we obtained spectra (red boxes).

For all the spectra we used GMOS-N with the 600 line\,mm$^{-1}$ grating designated G5307 and a GG455 cut-off filter to block second-order spectra.   The detector in both years was a mosaic of three e2v deep-depletion CCD chips, binned by 2 in the spatial direction (for a scale of 0\farcs 146 pixel$^{-1}$) and by 4 in the dispersion direction.  
The dispersion was 1.84 \AA\,  pixel$^{-1}$ (binned), resulting in coverage of the spectral range from at least \hb\ through \sii\lamlam 6716,\,6731 for virtually all the objects.\footnote{The detailed wavelength coverage for individual objects naturally varied with slitlet position in the dispersion direction.}  Our  masks had  slitlet  widths from 1\farcs 25 to 1\farcs 75, with wider slits used for the larger objects, and lengths of 6\arcsec\ or longer to permit local background and sky subtraction.

With each mask, we took spectra at three or four slightly different grating tilts, to cover wavelength gaps between chips and to gain somewhat more total spectral range.\footnote{An exception was mask 6, done late in the 2014B semester, for which our full set of planned observations were never completed.}  At each wavelength setting, we obtained two or more identical exposures to minimize the effects of cosmic rays.
For calibration, we programmed quartz flats and CuAr arc frames immediately before or after the science exposures with each mask and grating setting.  A journal of all the science observations from both 2014 and 2015 appears in Table \ref{obs_log}.

@@

The data were processed using standard procedures  from the {\tt gemini} package in IRAF  for bias subtraction, flat-fielding, wavelength calibration, and combination of spectra with different grating tilts to provide the final results.  
Flux calibration was based on baseline GMOS observations of a few spectrophotometric standard stars, carried out in the same semester as part of standard GMOS operations.  
%  IRAF footnote already given above, so I commented this out.  WPB
%\footnote{IRAF is distributed by the National Optical Astronomy Observatory, which is operated by the Association of Universities for Research in Astronomy, Inc., under cooperative agreement with the National Science Foundation.}  
During the processing, the 2-D spectra from different slitlets were separated to give individual 2-D spectra from each slitlet.   We examined each of these individually and selected the object region, as well as one or more sky background regions,  stripped out 1-D spectra of each, and then subtracted the sky spectrum from the corresponding object to obtain the final background-subtracted object spectra.  
Many of the objects are located in regions with bright surrounding galactic background (both continuum and emission lines) from NGC\,6946, so the selection of a representative local background was done on a best-effort basis.    In addition to the targeted SNR candidates and HII regions, we extracted spectra from other HII regions which appeared by chance in the slits when this was possible.   This allowed us to increase our sample of HII regions from 24 to 65.
We then performed  fits to obtain emission line fluxes  from the spectra, assuming Gaussian profiles.  We performed fits for various lines and line complexes:  \hb\ alone,  the \oiii\ doublet,  the \oi\ doublet,  the \ha-\nii\ region, and   the \sii\ doublet. For the fits, we assumed that the background varied linearly with wavelength around each line, and that the FWHM of all lines in each complex was the same.

Examples of the spectra that were obtained are shown in Fig.\ \ref{fig_example_spectra}.   The three SNRs were selected primarily to show how the quality of the spectra changes as a function of brightness.  The spectroscopically obtained [S II]:\ha\ ratio for L19-048 was 0.45, just above the value for spectroscopic confirmation, while those for the previously known bright object L19-097=MF-015 and the faint candidate L19-096 are higher.  All three SNR candidats show evidence of emission from [O I], which is another indicator that the emission we see arises from shock-heated gas.

Table \ref{table_snr_spec}  lists the information we obtained for the SNR candidates for which we obtained spectra.  Specifically we list (1) the source name, (2) the extracted  \ha\ flux, (3-9) ratios of various emission lines to \ha\ [taken to be 300], (10) the total \sii:\ha\ ratio and (11) the measured FWHM of the lines in the \ha-\nii\ complex.  For doublets, where the line ratio is constrained by atomic physics, that is \oiii, \oi, and \nii, we have listed only the stronger line.  We visually inspected all of the spectra and the fits to them; values which we judge to be more uncertain are indicated with tildes.  No allowance has been made for additional errors associated with difficulties in background subtraction.  A number of the objects were observed several times, sometimes with different slit orientations.  In these cases, we used the spectrum which we judged to be the most accurate and report it for reference in the `Spectrum' column in Table \ref{table_candidates}, where (for example) 05.18 should be interpreted as `mask 5 slitlet number 18.'

@@

\todo[inline]{Bill and Frank point out that various other diagrams with GC radius are missing, and in particular \sii:\ha\ ratio vs. \ha\ flux; \sii:\ha\ ratio vs. GCD (fig for this already here)  Check M83 to see if there is a correlation in the spectroscopic ratio with GCD, and if so comment on this.  This is done for S2; I guess we could to it for N2. Gradients: \nii:\ha\ and \sii:\ha\ vs GCD (M83 paper, fig 8) [WPB: Yes, I'd definitely like to see what this looks like.].  ksl: This is now provided, but whether these should be included is open to question.  If they are included some massaging of the plots is needed.  If included, Bill or Frank should provide words, and comparison to other galaxies}

>>>>

\newcommand{\EXPN}[2]{\mbox{$#1\times 10^{#2}$}}
\newcommand{\EXPU}[3]{\mbox{\rm $#1 \times 10^{#2} \rm\:#3$}}  % exponent with units
\newcommand{\POW}[2]{\mbox{$\rm10^{#1}\rm\:#2$}}

@@

\title{A New, Larger Sample of Supernova Remnants in NGC\,6946}

@@

The relatively nearby spiral galaxy NGC~6946 is one of the most actively star forming galaxies in the local Universe.  Ten supernovae (SNe) have been observed since 1917, and hence NGC~6946 surely contains a large number of supernova remnants (SNRs).  
Here we report a new optical search for these SNRs in NGC~6946 using narrow-band images obtained with the WIYN telescope.  We
identify 147 emission nebulae 
as likely SNRs,  based on elevated \sii:\ha\ ratios compared to \hii\ regions.  We have obtained spectra of 102 of these emission nebulae with Gemini North--GMOS; of these, 89 have \sii:\ha\ ratios greater than 0.4.  There is very little overlap in our sample between the SNR candidates identified  by Lacey et al. (2001) from radio data.  Very few of the SNR candidates are known X-ray sources, unlike the situation in some other galaxies such as M33 and M83.  The emission line ratios, e.g., \nii:\ha, of the candidates in NGC~6946 are typical of those observed in SNR samples from other galaxies with comparable metallicity.  
None of the  candidates observed in our low resolution spectra show evidence of anomalous abundances or  significant velocity broadening.   We also obtained new spectra of two of the historical SNe in NGC~6946, SN1980K and SN2004ET, both of which show high velocity ejecta. We did not detect emission from any of the other historical SNe.

@@

Optically, SNRs are usually identified on the basis of high \sii:\ha\ ratios compared to \hii\ regions.  In bright \hii\ regions, most S is found in the form of S$^{++}$ or S$^{+++}$, and as a result the \sii:\ha\ ratios are typically 0.1 or smaller.  In SNRs, where emission is driven by impulsive heating from shock waves, S$^+$ is found in an extended recombination and cooling zone behind the shock, and the \sii:\ha\ ratios are typically $\gtrsim0.4$.  The diagnostic can become less deterministic as one pushes to lower surface brightnesses, as recently discussed by \cite{long18} for the case of M33.

The first optical search for SNRs in \gal\ was made by \cite{matonick97}, hereafter MF97, who used interference filter imagery to identify 27 emission nebulae with \sii:\ha\ ratios $\geq$ 0.45 as SNRs.  One of these sources, MF97-16, was later associated with the ultraluminous black hole X-ray binary \gal\ X-1 \citep{roberts03}. Though very rare, such ultra-luminous X-ray sources (ULXs) have  the hard X-ray spectra that produce line ratios in the surrounding circumstellar ISM that resemble those expected from SNRs. To our knowledge, no other optical searches for SNRs in NGC~6946 exist, nor have spectra of the remaining MF97 objects ever been reported.

% \hii\ regions and SNRs also radiate at radio wavelengths.  SNRs typically have steep non-thermal radio spectral indices arising from synchrotron radiation, whereas \hii\ regions have relatively flat thermal spectra arising from free-free radiation.  At radio wavelengths, SNRs in nearby galaxies are generally identified as non-thermal radio sources associated with optical \ha\ emission.  (This association criterion arises because many background radio sources---typically active galaxy nuclei (AGNs)---also have non-thermal spectra, and like AGNs, the SNRs are generally unresolved in radio images of galaxies beyond the Local Group.)  In the case of \gal,  \cite{lacey01} identified 35 radio-selected SNR candidates on the basis of these criteria, none of which overlap with the MF97 list of optical candidates.  Their radio candidates were located in the brightest parts of the spiral arms of \gal; Lacey \& Duric suggested that the reason the two lists do not overlap is primarily due to selection effects.

Here we discuss a new, more sensitive optical search for SNRs in \gal\ in which we identify a total of 147 SNR candidates using interference filter imagery.  We also discuss spectroscopic observations of 102 of these candidates, which we use to verify the ratios obtained from the imaging and to characterize other characteristics of our new optical sample.  The paper is organized as follows:  Section 2 describes both our imaging and spectroscopy observations,  presents our significantly expanded catalog of optical SNR candidates, and the results of our spectroscopy.  Section 3 discusses these results in the context of both \gal\ and other spiral galaxies, and Section 4 provides a brief summary of our results.

@@

We carried out narrow-band imaging observations of \gal\ from the 3.5m WIYN telescope and MiniMosaic imager on Kitt Peak on the nights of 2011 June 26-28 (UT).\footnote{The WIYN Observatory is a joint facility of the University of Wisconsin-Madison, Indiana University, the National Optical Astronomy Observatory and the University of Missouri.}  The so-called ``Minimo'' was mounted at the f/6.3 Nasmyth port and consisted of a pair of $2048\times4096$ SITe chips, with a field  9\farcm 6 square at a scale of 0\farcs 14 pixel$^{-1}$.  We used interference filters that pass lines of \ha, \sii \lamlam6716,6731, and \oiii \lam 5007, plus red and green narrow-band continuum filters so we could subtract the stars and produce pure emission-line images. Frames in each filter were dithered to enable automatic removal of cosmic rays and bad pixels.  Further observational details are given in Table 1.  It is noteworthy that the \ha\ filter was quite narrow in bandwidth, 27\ \AA\ FWHM. Its transmission is 69\% at the rest wavelength of \ha, but only 11\% at 6548\ \AA\ and 16\% at 6583\ \AA; hence, the \nii\ lines are greatly attenuated relative to \ha.\footnote{The recessional velocity of \gal\ is only $40 \kms$, so the lines are redshifted by $\lesssim 1$ \AA.}  This facilitates identification of SNRs based on their image-derived \sii:\ha\ ratios.  Seeing throughout this run was about $1\arcsec \approx 32$ pc at the distance of \gal.  While sufficient for identifying SNRs in all but the most crowded regions, this resolution was insufficient for obtaining properties such as diameter or morphology.

We used standard IRAF\footnote{IRAF is distributed by the National Optical Astronomy Observatory, which is operated by the Association of Universities for Research in Astronomy, Inc., under cooperative agreement with the National Science Foundation.} techniques for processing the images, including overscan correction, bias subtraction, and flat-fielding using dome flats.  Procedures in the IRAF {\texttt mscred} package were then used to combine the data from the individual chips into a mosaic image for each frame, assigned a WCS for each using stars from the USNOB1 catalog \citep{monet03}.  We then stacked  all the images by filter onto an arbitrary standard coordinate system with a scale of 0\farcs 20 pixel$^{-1}$ and scaled and subtracted the continuum images from the emission-line ones (red from \ha\ and \sii; green from \oiii) to give pure emission-line images with most of the stars and galaxy background light removed.  Finally, we used observations of several spectrophotometric standard stars from the catalog of \citet{massey88} to flux calibrate the emission-line images.  Figure \ref{fig_rgb_overview} shows a color version of the final images (R = \ha, G = \sii, B = \oiii), with the positions of historical SNe in \gal\ also indicated.

@@

To select SNR candidates, we used the DS9 display program to show the continuum-subtracted WIYN images in all three emission lines as well as a \sii:\ha\ ratio image and a continuum image (to discriminate stars or stellar subtraction residuals from point-like nebulae).   We then visually inspected these to select SNR candidates based on a high \sii:\ha\ ratio.  The initial inspection was carried out by Middlebury undergraduate Marc DeLaney; subsequently two of us (WPB and PFW) compiled independent candidate lists; we then conferred to agree on a consensus list of 147 candidates, including the 27 from MF97. The positions of all 147 candidates are shown in Figure ~\ref{fig_index_overview}. The vast majority of the SNR candidates appear within the spiral arms or clustered on the outskirts of large complexes of \hii\ emission and star formation.

Figure \ref{fig_diagnostic} shows an example for a small region $\sim$1.5\arcmin\ south of the nucleus (see Fig. ~\ref{fig_index_overview}) containing two of the MF97 objects and several new SNR candidates. In this example we have combined the three continuum-subtracted emission line images into a single color panel that shows how the stronger \sii\ and/or \oiii\ emission from the SNR candidates makes them stand out.  The \sii:\ha\ ratio image was a key diagnostic for drawing our eyes to potential objects of interest. Then an assessment of the integrity of the candidate as an emission object was made by inspection of the actual images.  This was done to separate candidates from stellar residuals or false regions of higher ratio in the ratio map that were due to noise.

Having performed similar SNR searches in other galaxies such as M33 and M83, it is worth noting some differences for \gal.  M33 is of course much closer, and the nebulae of interest are almost always resolved.  M83 is much more distant (4.6 Mpc) than M33, but our search there was aided by the exceptional seeing conditions we obtained at the Magellan telescope (0.5\arcsec) \citep{blair12}.  Many objects were resolved, but others extended down to the limits of what even HST could resolve ($\sim$1-2 pc) \citep{blair14}.  Our WIYN survey of \gal\ did not have exceptional seeing, and the distance is some 50\% larger than for M83.  Hence, relatively few of the nebulae of interest are resolved, and with variations in the complex galaxy background, it is much more difficult to perform a systematic search.  The use of the \sii:\ha\ ratio image was particularly helpful for \gal, which is the most distant galaxy for which we have performed this kind of ground-based SNR survey. Nonetheless, while we have expanded the SNR candidate list very substantially, clearly completeness has not been achieved.  Our list of 147 SNR candidates falls far short of M83 for example (with 300+), even though the SN rate is larger in \gal.  Higher resolution data (better seeing and/or HST imaging) would no doubt help substantially, but the greater distance for \gal\ is still a limiting factor.

In addition, we initially selected 51 emission nebulae with relatively high \oiii:\ha\ ratios (using an \oiii:\ha\ ratio image in the display).  Most, if not all, of these nebulae were expected to be \hii\ regions but we hoped that one or more of these regions might be a young, ejecta-dominated SNR, simlar to Cas A in the Galaxy. With ten SNe in the last century and a high incidence of massive stars, one might expect a number of young, ejecta-dominated SNRs to be present.  Though none of the O-selected candidates had ratios as extreme as seen for Cas A or 1E0102-72.3 in the Small Magellanic Cloud, we nevertheless selected some of these for follow-up spectroscopy.  None of these nebulae for which we obtained spectra have any indication of ejecta in their spectra or the broad lines would expect from a very young SNR.  All are \hii\ regions with somewhat enhanced ionization state, and so these form the bulk of the \hii\ sample we use for comparison with the SNR candidates sample below. Finally, we inspected the positions of the nine\footnote{As of the 2011 observations there were nine SNe; a tenth SN was recorded in 2017.} historical SNe in \gal\ for evidence of nebular emission; we only detected line emission at the positions of SN1980K and SN2004et, both of which we targeted for follow-up spectroscopy. (See section 3.4 below.)

%\todo[inline]{ksl - It might be worthwhile to have a few sentences of comparison here to our work on M83 where the Magellan seeing made if far easier to see extended emission, and in M33 of course where all of the SNRs are resolved.  This is about the limit of what we can do from the ground, particularly with the seeing we had with WYIN.  To do better, one needs better seeing.  WPB: I tried to incorporate these points into the text added above with the example diagnostic figure.}

The SNR candidates are listed in Right Ascension order in Table \ref{table_candidates}.  For each candidate, we provide (1) a source name, (2,3) the position  (J2000), (4) the deprojected galactocentric distance (GCD), (5) the \ha\ flux as derived from the emission line images, (6) the \sii:\ha\ ratio measured from the images, (7) the spectrum we used to confirm the imaging ratios (see below), (8) whether or not the object has a spectroscopic confirmation that the  \sii:\ha\ ratio is $\ge$ 0.4 (see below) and (9) other names for the source.

% \todo[inline]{We need a consistent story about the HII regions.  We mention that we selected some O3 objects.  We got spectra of 24 of these.   We have another 41 spectra of HII regions along the slit.  We got very few HII regions just by chance, though these are included in the 41.  It's hard to actually parse out the history of which are which.  WPB: Note that I added some words above in the ``[O III] object" discussion to at least partially address this concern.}

@@

We used the Gemini Multi-Object Spectrograph (GMOS) on the 8.2m Gemini-North telescope to obtain all the spectra reported here, during queue-scheduled programs in semesters 2014B (program GN-2014B-Q-83) and 2015B (program GN-2015B-Q-91).  
For the 2014B program, we designed six custom masks, each with 20-30 slitlets targeting SNR candidates whose positions we determined from our 2011 WIYN images, together with  short $R$-band pre-images of several \gal\ fields taken with GMOS earlier in 2014 as part of the spectroscopy preparation program.    
We used two additional masks (which we refer to as masks 7 and 8 for simplicity)  for the 2015B program.  Slitlets in one or more of our eight masks were placed on 102 distinct SNR candidates, including ones with a range of sizes, GCDs, and ISM environments (locations in arms and in 
inter-arm regions).  In addition to the SNR candidates, we also placed a number of slitlets on \hii\ regions for comparison purposes in both 2014 and 2015.
% Next sentence redundant with below, so commented out here.  WPB
%Figure \ref{fig_index_overview} shows all the SNR candidates from the sample for which we obtained spectra (red boxes).

For all the spectra we used the 600 line\,mm$^{-1}$ grating designated G5307 and a GG455 cut-off filter to block second-order spectra.   The detector in both years was a mosaic of three e2v deep-depletion CCD chips, binned by 2 in the spatial direction (for a scale of 0\farcs 146 pixel$^{-1}$) and by 4 in the dispersion direction.  
The dispersion was 1.84 \AA\,  pixel$^{-1}$ (binned), resulting in coverage of the spectral range from at least \hb\ through \sii\lamlam 6716,\,6731 for virtually all the objects.\footnote{The detailed wavelength coverage for individual objects naturally varied with slitlet position in the dispersion direction.}  Our  masks had  slitlet  widths from 1\farcs 25 to 1\farcs 75, with wider slits used for the larger objects, and lengths of 6\arcsec\ or longer to permit local background and sky subtraction.

With each mask, we took spectra at three or four slightly different grating tilts, to cover wavelength gaps between chips and to gain somewhat more total spectral range.\footnote{An exception was mask 6, done late in the 2014B semester, for which our full set of planned observations were never completed.}  At each wavelength setting, we obtained two or more identical exposures to minimize the effects of cosmic rays.
For calibration, we programmed quartz flats and CuAr arc frames immediately before or after the science exposures with each mask and grating setting.  A journal of all the science observations from both 2014 and 2015 appears in Table \ref{obs_log}.  The SNR candidates for which we obtained spectra are indicated by the small red boxes in Fig.~\ref{fig_index_overview}.

@@

The data were processed using standard procedures  from the {\tt gemini} package in IRAF  for bias subtraction, flat-fielding, wavelength calibration, and combination of spectra with different grating tilts to provide the final results.  
Flux calibration was based on baseline GMOS observations of a few spectrophotometric standard stars, carried out in the same semester as part of standard GMOS operations.  
%  IRAF footnote already given above, so I commented this out.  WPB
%\footnote{IRAF is distributed by the National Optical Astronomy Observatory, which is operated by the Association of Universities for Research in Astronomy, Inc., under cooperative agreement with the National Science Foundation.}  
During the processing, the 2-D spectra from different slitlets were separated to give individual 2-D spectra from each slitlet.   We examined each of these individually and selected the object region, as well as one or more sky background regions,  stripped out 1-D spectra of each, and then subtracted the sky spectrum from the corresponding object to obtain the final background-subtracted object spectra.  
Many of the objects are located in regions with bright surrounding galactic background (both continuum and emission lines) from NGC\,6946, so the selection of a representative local background was done on a best-effort basis.    In addition to the targeted SNR candidates and \hii\ regions, we extracted spectra from other \hii\ regions which appeared by chance in the slits when this was possible.   This allowed us to increase our sample of \hii\ regions from 24 to 65.
We then performed  fits to obtain emission line fluxes  from the spectra, assuming Gaussian profiles, for the following lines and line complexes:  \hb\ alone,  the \oiii\ doublet,  the \oi\ doublet,  the \ha-\nii\ region, and   the \sii\ doublet. For the fits, we assumed that the background varied linearly with wavelength around each line, and that the FWHM of all lines in each complex was the same.

Representative examples of the spectra that were obtained are shown in Fig.\ \ref{fig_example_spectra}.   The three SNRs were selected primarily to show how the quality of the spectra changes as a function of brightness.  The spectroscopically obtained \sii:\ha\ ratio for L19-048 was 0.45, just above the value for spectroscopic confirmation, while those for the previously known bright object L19-097=MF-015 and the faint candidate L19-096 are higher.  All three SNR candidates show evidence of emission from [O I], which is another indicator that the emission we see arises from shock-heated gas.

Table \ref{table_snr_spec}  lists the information we obtained for the SNR candidates for which we obtained spectra.  Specifically we list (1) the source name, (2) the extracted  \ha\ flux, (3-9) ratios of various emission lines to \ha\ [taken to be 300], (10) the total \sii:\ha\ ratio and (11) the measured FWHM of the lines in the \ha-\nii\ complex.  For doublets, where the line ratio is constrained by atomic physics, that is \oiii, \oi, and \nii, we have listed only the stronger line.  We visually inspected all of the spectra and the fits to them; values which we judge to be more uncertain are indicated with tildes in the Table.  No allowance has been made for additional errors associated with difficulties in background subtraction.  A number of the objects were observed with more than one mask, sometimes with different slit orientations.  In these cases, we used the spectrum which we judged to be the most accurate and report it for reference in the `Spectrum' column in Table \ref{table_candidates}, where (for example) 05.18 should be interpreted as `mask 5 slitlet number 18.'

@@

%\todo[inline]{Frank and Bill have suggested that we do the comparison to models figures in the same way we did for M33 in L18, which includes plots not only of the models but also of where these ratios lie in other galaxies. See Figures 10 and 11 of L18. Bill also thinks the ratios are less than in M83 and wonders why that might be.  WPB: I have added some additional comments below, and am retiring this comment. }

% \todo[inline]{Bill and Frank point out that various other diagrams with GC radius are missing, and in particular \sii:\ha\ ratio vs. \ha\ flux.  If included, Bill or Frank should provide words, and comparison to other galaxies.}

Our SNR line ratios show a  trend of decrease with increasing GCD as seen in Fig. \ref{fig_metal_ratios}, although the dispersion at any particular GCD distance is large.  The trend could well be indicative of abundances gradients in N and S, with the dispersion being due to varying shock conditions and/or or local abundance variations.  However, the trend stands in contrast to SNRs in M33, where both the \nii:\ha\ and \sii:\ha\ ratios have a large range and do not decrease systematically with increasing GCD (although the line ratios in the \hii\ region sample appear well behaved--see L18 Fig. 8).   There is a good correlation between the \nii:\ha\ and \sii:\ha\ ratios of the various objects, as shown in  Fig. \ref{fig_s2_n2}, as also seen in other galaxy samples (cf. Winkler et al. 2017, Fig. 9).
